Conference Paper Title\\

### 2023-06-14 LARS_paper/paper.tex
Fix text

\begin{abstract}
  With the growth of robotics, mobile robots are increasingly becoming common in key sectors of the economy. When compared to wheeled and tracked robots, legged robots present greater mobility and maneuverability, but less locomotion stability, which in turn demands more complex control systems. This paper aims to develop a quadruped robot and a PID  stabilization controller to compensate for the body oscillation during the walk. This work presents the development of the mobile robot platform, including the prototype, the gait planner, the kinematic model, and the control subsystem. Finally, locomotion experiments were conducted to assess the robot's locomotion performance when using the stabilization controller. The experiments were realized in terrains flat and uneven. Therefore, it was observed that the stabilization controller contributed to reducing the oscillation of the robot's body in both roll and pitch during walking in both terrains.
\end{abstract}

@@

This paper is divided as follows: section \ref{development} presents the development of the robot, focusing on the gait planner, the kinematic model, the stabilization control and the trajectory planner implementations. In section \ref{results}, the experiments conducted to evaluate and validate the effectiveness of the designed controller through statistical analysis are explained. Finally, section \ref{conclusion} presents the conclusions and suggestions for future work.

@@

The robot platform designed and developed for this research is presented in the Fig. \ref{fig:robot}.

\begin{figure}[!htb]
  \centering
  \caption{The quadruped robot developed for this research}
  \includegraphics[width=0.25\textwidth]{robot.jpeg}
  \vfill
  % \vspace{-\baselineskip}
  \label{fig:robot}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \caption{Gait pattern diagram}
  \includegraphics[width=0.45\textwidth]{trot_pattern.png}
  \vfill
  % \vspace{-\baselineskip}
  \label{fig:trot_pattern}
\end{figure}

@@

\begin{figure*}[h]
  \centering
  \begin{subfigure}[t]{0.32\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{Cycloid_space.png}
    \caption{The cycloidal curve in 3D space.}
    \label{fig:traj_space}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{Cycloid_time.png}
    \caption{The cycloidal curve in the time.}
    \label{fig:traj_time}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{Cycloid_modified.png}
    \caption{The curve with the distribution of points modified.}
    \label{fig:traj_time_modified}
  \end{subfigure}
  \vfill
  \caption{Cycloidal trajectories by the trajectory planner.}
  Fonte: autores.
  \label{fig:traj_curve}
\end{figure*}

@@

The joints' controllers is the Joint Trajectory Controller, a controller of ROS which executes joint-space trajectories on a group of joints. According to REF, trajectories are specified as a set of waypoints to be reached at specific time instants, which the controller attempts to execute as well as the mechanism allows. In this work, the waypoints consist of positions and are reached using PID controllers loop-closed.

@@

\begin{figure}[!htb]
  \centering
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{plane_boxplot.png}
    \caption{Flat terrain.}
    \label{fig:imu_test_plane}
  \end{subfigure}
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{irregular_boxplot.png}
    \caption{Uneven terrain.}
    \label{fig:imu_test_irregular}
  \end{subfigure}
  \caption{Robot body's oscillation in both terrains
  Oscilação do corpo em ambos os tipos de terreno.}
  Fonte: autores.
  \label{fig:imu_test}
\end{figure}

>>>>

\begin{abstract}
  With the growth of robotics, mobile robots are increasingly becoming common in key sectors of the economy. When compared to wheeled and tracked robots, legged robots present greater mobility and maneuverability, but less locomotion stability, which in turn demands more complex control systems. This paper aims to develop a quadruped robot and a PID  stabilization controller to compensate for the body oscillation during the walk, for that, the gait planner and the kinematic model algorithm were implemented. Finally, locomotion experiments were conducted to assess the robot's locomotion performance when using the stabilization controller. The experiments were realized in flat and uneven terrains. It was observed that the stabilization controller contributed to reducing the oscillation of the robot's body in both roll and pitch angles during walking in both terrains.
\end{abstract}

@@

This paper is divided as follows: section \ref{development} presents the development of the robot. In section \ref{results}, the experiments conducted to evaluate and validate the effectiveness of the designed controller through statistical analysis are explained. Finally, section \ref{conclusion} presents the conclusions and suggestions for future work.

@@

The robot platform designed for this research is presented in the Fig. \ref{fig:robot}. The development encompassed the prototyping and the implementation of the gait planner, the trajectory planner, the kinematic model, and the control subsystem.

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.25\textwidth]{robot.jpeg}
  \vfill
  % \vspace{-\baselineskip}
  \caption{The quadruped robot}
  \label{fig:robot}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.45\textwidth]{trot_pattern.png}
  \vfill
  % \vspace{-\baselineskip}
  \caption{Gait pattern diagram}
  \label{fig:trot_pattern}
\end{figure}

@@

\begin{figure*}[h]
  \centering
  \begin{subfigure}[t]{0.32\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{Cycloid_space.png}
    \caption{The cycloidal curve in 3D space.}
    \label{fig:traj_space}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{Cycloid_time.png}
    \caption{The cycloidal curve in the time.}
    \label{fig:traj_time}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{Cycloid_modified.png}
    \caption{The curve with the distribution of points modified.}
    \label{fig:traj_time_modified}
  \end{subfigure}
  \vfill
  \caption{Cycloidal trajectories by the trajectory planner.}
  \label{fig:traj_curve}
\end{figure*}

@@

The joints' controllers is the Joint Trajectory Controller, a controller of ROS which executes joint-space trajectories on a group of joints. According to \cite{joint-trajectory}, trajectories are specified as a set of waypoints to be reached at specific time instants, which the controller attempts to execute as well as the mechanism allows. In this work, the waypoints consist of positions and are reached using PID controllers loop-closed.

@@

\begin{figure}[!htb]
  \centering
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{plane_boxplot.png}
    \caption{Flat terrain.}
    \label{fig:imu_test_plane}
  \end{subfigure}
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{irregular_boxplot.png}
    \caption{Uneven terrain.}
    \label{fig:imu_test_irregular}
  \end{subfigure}
  \caption{Robot body's oscillation in both terrains.}
  \label{fig:imu_test}
\end{figure}
